HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-05-04 LaTeX/ms.tex
Bug fix in table 1 and 3
Plus other minor changes.

\slugcomment{To be submitted to the ApJ}

@@

M.~Jarvis\altaffilmark{17},

@@

I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},

@@

\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}

@@

{\bf HECDFS12:} This is a complex, well-constrained system.  Two background
sources are detected by ALMA: one is multiply imaged and the other is singly
imaged.  In addition, the lens is detected by ALMA (this is one of two sources
in the entire {\it Herschel}-ALMA sample that is unresolved by ALMA).  These
facts work together to provide very tight constraints on the system.  Since the
lens is detected by ALMA, its position relative to the lensed images is
unambiguous.  Also, because there is a strongly lensed source with multiple
images, the Einstein radius of the lens is unambiguous.  A byproduct of these
two facts is that the magnification factor of the weakly lensed source is known
to very high precision as well.  It experiences a magnification factor of
$\mu_{870} = 1.520\pm0.002$ (note that this error bar is valid under the
assumptions of our model, most notably the assumption that the singly imaged
source is located at the same redshift as the multiply imaged source; the true
uncertainty is likely a factor of a few larger).  despite being located
$\approx4\arcsec$ north of the lens (which has an Einstein radius of
$1.353\pm0.005$; it is the tight constraint on the Einstein radius that permits
such a tight constraint on $\mu_{870}$ for the weakly lensed source).  We use
these numbers to inform our estimates of the Einstein radius for weakly lensed
sources without the excellent contraints provided by this system.  Finally,
this source is detected (and unresolved) in the NRAO VLA Sky Survey
\citep{Condon:1998uq}, having $S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming
all of this radio emission originates from the lens, this implies a spectral
slope of $\alpha = -0.24$ and is consistent with non-thermal emission from the
lens.

@@

The National Radio Astronomy Observatory is a facility of the National Science
Foundation operated under cooperative agreement by Associated Universities,
Inc.  The Dark Cosmology Centre is funded by the Danish National Research
Foundation.

@@

R.J.I. acknowledges support from European Research Council Advanced
Investigator Grant, Cosmicism, 321302. C.C.H. is grateful to the Gordon and
Betty Moore Foundation for financial support.

@@

%\bibliography{rbussman}
\begin{thebibliography}{106}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

>>>>

\slugcomment{Submitted to the ApJ}

@@

M.~Jarvis\altaffilmark{17,18},

@@

I.~P{\'e}rez-Fournon\altaffilmark{19,20},
D.~Rigopoulou\altaffilmark{21,17},

@@

\altaffiltext{17}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{18}{Astrophysics Group, Physics Department, University of the Western Cape, Private Bag X17, 7535, Bellville, Cape Town, South Africa}
\altaffiltext{19}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{20}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{21}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}

@@

{\bf HECDFS12:} This is a complex, well-constrained system.  Two background
sources are detected by ALMA: one is multiply imaged and the other is singly
imaged.  In addition, the lens is detected by ALMA (this is one of two sources
in the entire {\it Herschel}-ALMA sample that is unresolved by ALMA).  These
facts work together to provide very tight constraints on the system.  Since the
lens is detected by ALMA, its position relative to the lensed images is
unambiguous.  Also, because there is a strongly lensed source with multiple
images, the Einstein radius of the lens is unambiguous.  A byproduct of these
two facts is that the magnification factor of the weakly lensed source is known
to very high precision as well.  It experiences a magnification factor of
$\mu_{870} = 1.520\pm0.002$ (note that this error bar is valid under the
assumptions of our model, most notably the assumption that the singly imaged
source is located at the same redshift as the multiply imaged source; the true
uncertainty is likely a factor of a few larger).  despite being located
$\approx4\arcsec$ north of the lens (which has an Einstein radius of
$1.353\pm0.005$; it is the tight constraint on the Einstein radius that permits
such a tight constraint on $\mu_{870}$ for the weakly lensed source).  We use
these numbers to inform our estimates of the Einstein radius for weakly lensed
sources without the excellent contraints provided by this system.  Finally,
this source is detected (and unresolved) in the NRAO VLA Sky Survey
\citep{Condon:1998uq}, having $S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming
all of this radio emission originates from the lens, this implies a spectral
slope of $\alpha = -0.24$ and is consistent with non-thermal emission from the
lens.  For this target, we show VIDEO $K_{\rm s}$ imaging
\citep{Jarvis:2013lr}.

@@

The VIDEO imaging data are based on data products from observations
made with ESO Telescopes at the La Silla or Paranal Observatories under ESO
programme ID 179.A-2006.

@@

The National Radio Astronomy Observatory is a facility of the National Science
Foundation operated under cooperative agreement by Associated Universities,
Inc.  The Dark Cosmology Centre is funded by the Danish National Research
Foundation. R.J.I. acknowledges support from European Research Council Advanced
Investigator Grant, Cosmicism, 321302. C.C.H. is grateful to the Gordon and
Betty Moore Foundation for financial support.

@@

%\bibliography{rbussman}
\begin{thebibliography}{107}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[{{Jarvis} {et~al.}(2013){Jarvis}, {Bonfield}, {Bruce}, {Geach},
  {McAlpine}, {McLure}, {Gonz{\'a}lez-Solares}, {Irwin}, {Lewis}, {Yoldas},
  {Andreon}, {Cross}, {Emerson}, {Dalton}, {Dunlop}, {Hodgkin}, {Le},
  {Karouzos}, {Meisenheimer}, {Oliver}, {Rawlings}, {Simpson}, {Smail},
  {Smith}, {Sullivan}, {Sutherland}, {White}, \& {Zwart}}]{Jarvis:2013lr}
{Jarvis}, M.~J., {Bonfield}, D.~G., {Bruce}, V.~A., {Geach}, J.~E., {McAlpine},
  K., {McLure}, R.~J., {Gonz{\'a}lez-Solares}, E., {Irwin}, M., {Lewis}, J.,
  {Yoldas}, A.~K., {Andreon}, S., {Cross}, N.~J.~G., {Emerson}, J.~P.,
  {Dalton}, G., {Dunlop}, J.~S., {Hodgkin}, S.~T., {Le}, F.~O., {Karouzos}, M.,
  {Meisenheimer}, K., {Oliver}, S., {Rawlings}, S., {Simpson}, C., {Smail}, I.,
  {Smith}, D.~J.~B., {Sullivan}, M., {Sutherland}, W., {White}, S.~V., \&
  {Zwart}, J.~T.~L. 2013, \mnras, 428, 1281
